Clause size reduction with all-UIP Learning

### 2020-02-24 paper.tex

%\begin{figure} 
%\begin{center} 
%\begin{tabular}{ | m{3.5cm} | m{5cm}| m{3.5cm} | } 
%\hline
%Solver & $\allUip$ attempt rate & $\allUip$ success rate  \\ 
%\hline
%$\MapleIUIPPure$ & 16.1\% & 43.4\% \\ 
%\hline
%$\MapleIUIMin$ & 28.8\% & 59.3\% \\ 
%\hline
%\end{tabular}
%\end{center}
%\caption{Compare $\allUipPure$ and $\allUipMin$ i-uip attempt rate and success rate. %$\allUipMin$ scheme attempted $\allUip$ more frequently, and it is more likely to %successfully produce smaller $C_i$ clause .}
%\label{fig:t2}
%\end{figure}
\subsubsection{Reduced Proof sizes with $\allUip$.}
A learning scheme that yields smaller clauses (lemmas) might also
construct smaller causal proofs. For UNSAT instances, we additionally
compare the size of the optimized DRAT proof from $\allUipPure$,
$\allUipMin$ and 1-UIP schemes. We used the DART-trim tool
\cite{wetzler2014drat} with a 10000 second timeout to check and
optimize every DRAT proof once \footnote{Applying DART-trim multiple
  times can further reduce the proof size until a fix-point. However,
  the full optimization is time consuming and was impractical for our
  experiments.}.

@@

\subsubsection{$\allUip$ on Modern SAT solvers}
To validate $\allUip$ as a practical learning scheme for modern SAT
solvers, we implemented $\allUip$ in the winners of 2017, 2018 and
2019 SAT
Race\cite{luo2017effective,ryvchin2018maple,Stepan2019MapleLCMDistChronoBT}
and in the $\expSAT$\cite{MdSolimul2019expMalpe} ($\expSATShort$)
solver. $\expSATShort$ is a top ten solver from 2019 SAT race which
uses random walk simulation to help branching. We chose $\expSATShort$
because (1) it one of the top solvers in the 2019 SAT Race that does
not use chronological backtracking; and (2) the random walk simulation
branching heuristic is different from local branching heuristic (VSIDS
and LRB) that we have considered in $\allUipAct$, $\allUipIn$, and
$\allUipEx$. We compared these solver's base 1-UIP learning scheme
with $\allUipPure$, $\allUipMin$ and the top two $\allUip$ variants,
$\allUipAct$ and $\allUipIn$, on the SAT Race 2019 main track
benchmark. We report solved instances, PAR-2 score and the average
clause size.

>>>>

%\begin{figure} 
%\begin{center} 
%\begin{tabular}{ | m{3.5cm} | m{5cm}| m{3.5cm} | } 
%\hline
%Solver & $\allUip$ attempt rate & $\allUip$ success rate  \\ 
%\hline
%$\MapleIUIPPure$ & 16.1\% & 43.4\% \\ 
%\hline
%$\MapleIUIMin$ & 28.8\% & 59.3\% \\ 
%\hline
%\end{tabular}
%\end{center}
%\caption{Compare $\allUipPure$ and $\allUipMin$ i-uip attempt rate and success rate. %$\allUipMin$ scheme attempted $\allUip$ more frequently, and it is more likely to %successfully produce smaller $C_i$ clause .}
%\label{fig:t2}
%\end{figure}

\subsubsection{Reduced Proof sizes with $\allUip$.}
A learning scheme that yields smaller clauses (lemmas) might also
construct smaller causal proofs. For UNSAT instances, we additionally
compare the size of the optimized DRAT proof from $\allUipPure$,
$\allUipMin$ and 1-UIP schemes. We used the DART-trim tool
\cite{DBLP:conf/sat/WetzlerHH14} with a 10000 second timeout to check and
optimize every DRAT proof once \footnote{Applying DART-trim multiple
  times can further reduce the proof size until a fix-point. However,
  the full optimization is time consuming and was impractical for our
  experiments.}.

@@

\subsubsection{$\allUip$ on Modern SAT solvers}
To validate $\allUip$ as a practical learning scheme for modern SAT
solvers, we implemented $\allUip$ in the winners of 2017, 2018 and
2019 SAT
Race\cite{DBLP:conf/ijcai/LuoLXML17,ryvchin2018maple,Stepan2019MapleLCMDistChronoBT}
and in the $\expSAT$\cite{MdSolimul2019expMalpe} ($\expSATShort$)
solver. $\expSATShort$ is a top ten solver from 2019 SAT race which
uses random walk simulation to help branching. We chose $\expSATShort$
because (1) it one of the top solvers in the 2019 SAT Race that does
not use chronological backtracking; and (2) the random walk simulation
branching heuristic is different from local branching heuristic (VSIDS
and LRB) that we have considered in $\allUipAct$, $\allUipIn$, and
$\allUipEx$. We compared these solver's base 1-UIP learning scheme
with $\allUipPure$, $\allUipMin$ and the top two $\allUip$ variants,
$\allUipAct$ and $\allUipIn$, on the SAT Race 2019 main track
benchmark. We report solved instances, PAR-2 score and the average
clause size.
